---
title: "Writing Functions"
author: "Yue Liu"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---
List columns are very useful
imagine you have an input list in a data frame
You can map a function to each element of that input list, export the output list, and save it in the same data frame

Imagine you have granular data nested within large units
- make a list storing your granular data table
- add the granular data table list to a data frame containing data on larger units 
Why stop?
- you can store more complex R objects, like output from regressions on each granular data table in a list 
- you can add that list to your data frame

Keeping everything in one data frame with list columns means there are fewer things to worry about

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Lists 

You can put anything in a list.

```{r}
l = list(
  vec_numeric = 5:8,
  vec_logical = c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
  mat = matrix(1:8, nrow = 2, ncol = 4),
  summary = summary(rnorm(100))
)
```

```{r}
l$vec_numeric
l[[1]]
mean(l[["vec_numeric"]])
```

## `for` loop

Create a new list.

```{r}
list_norm = 
  list(
    a = rnorm(20, mean = 3, sd = 1),
    b = rnorm(30, mean = 0, sd = 5),
    c = rnorm(40, mean = 10, sd = 0.2),
    d = rnorm(20, mean = -3, sd = 1)
  )
```

```{r}
list_norm
```

Pause and get my old function

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x) < 3){
    stop("Input must have at least three numbers ")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean =  mean_x,
    sd = sd_x
  )

}
```

```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])
```

Let's use a for loop:

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norm[[i]])
  
}
```

## Let's try map!

```{r}
map_output = map(list_norm, mean_and_sd)
# similar as the for loop output
```

What if you want a different function..?

```{r}
output = map(list_norm, IQR) # can be a standard function as well
```

